Local Search Approximation Algorithms for Partitional and Hierarchical Clustering

### 2015-05-10 tex/project.tex
Project write-up

We implemented the local search swapping algorithm described above for $p=1, 2, 3$ as well as the supermodular function minimization algorithm in Python and compare against $k$-means, $k$-medoids and Shi and Meila's spectral algorithm (implemented in the scikit-learn package for Python).  We also implemented the $k$-medoids algorithm with a maximum iteration of 1000. Note that for $p=1$, the multiswaps algorithm is equivalent to the well-known PAM algorithm.  In order to calculate approximation ratios, Gurobi was used to compute the global optimum for each data set.

@@

For each data set and each clustering method, we report the approximation ratio, computation time, and adjusted mutual information (AMI).  AMI is a measure which scores accuracy of predicted clusters compared to a true labeling by measuring the agreement of two assignments. The measure is normalized to reflect chance, so that a perfect labeling receives a score of 1 and an independent random labeling receives a score of 0 in expectation.  See \cite{Vinh} for further information.  The results reported are average values across 10 trials.

>>>>

We implemented the local search swapping algorithm described above for $p=1, 2, 3$ as well as the supermodular function minimization algorithm in Python, and compare against $k$-means, $k$-medoids and Shi and Meila's spectral algorithm (implemented in the scikit-learn package for Python).  We also implemented the $k$-medoids algorithm with a maximum iteration of 1000. Note that for $p=1$, the multiswaps algorithm is equivalent to the well-known PAM algorithm.  In order to calculate approximation ratios, Gurobi was used to compute the global optimum for each data set.

@@

For each data set and each clustering method, we report objective function values, the approximation ratio, computation time, and adjusted mutual information (AMI).  AMI is a measure which scores accuracy of predicted clusters compared to a true labeling by measuring the agreement of two assignments. The measure is normalized to reflect chance, so that a perfect labeling receives a score of 1 and an independent random labeling receives a score of 0 in expectation.  See \cite{Vinh} for further information.  The results reported are average values across 10 trials.
